Create Regression Data

### 2022-04-24 data-cleaning/08-create-regression-data.Rmd
one measure per frame

case_level <- box_read("947450386335")
justice_level <- box_read("947810760828")
```

@@

```{r}
case_level <- case_level %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
  pivot_wider(., c(case,author_type),
              names_from = author_type,
              values_from=c(abortion_different:womens_rights),
              names_glue = "{author_type}_{.value}") %>% 
  select(case, sort(colnames(.)))

@@

>>>>

case_amici_level <- box_read("947450386335")
justice_level <- box_read("947810760828")
```

@@

```{r}
case_level <- case_amici_level %>% 
  rename_with(.cols=contains("freq"), .fn=~sub("_freq.*", "", .x)) %>% 
  pivot_wider(., c(case,author_type),
              names_from = author_type,
              values_from=c(abortion_different:womens_rights),
              names_glue = "{author_type}_{.value}") %>% 
  select(case, sort(colnames(.)))

@@

# One measure per frame

Instead of looking at measures by author type, look at aggregation of measures.

```{r}
case_amici_level <- case_amici_level %>% 
  mutate(case = str_replace(case, 'v\\.', 'v'),
        case = str_replace_all(case, "(,|’|'|\\)|\\()", ""))

# sum up frequencies by frame
case_amici_level <- case_amici_level %>% group_by(case) %>% 
  summarize(across(contains("freq"), ~ sum(.x, na.rm = TRUE)))

final <- case_amici_level %>% 
  left_join(., justice_level, by = "case") %>% 
  select(case, ddate2:cirsplit, everything())
```

Save

```{r}
box_write(final,
          file_name = "amicus-iv-regression-data-frame-by-case-amici-only.csv",
          dir_id = 158993526875)
```
